\documentclass[letterpaper,twocolumn]{article}

\usepackage[margin=2cm]{geometry}
\emergencystretch=1em

\usepackage{graphicx}
\usepackage{color}
\usepackage[font=small]{caption}
\usepackage{subcaption}

\usepackage{hyperref}
\usepackage{url}

\renewcommand*{\familydefault}{\sfdefault}	%sans serif

\begin{document}

\title{Springs of Water in a Parched Land}
\author{Brian Plimley}
\date{\today}
\maketitle

\setcounter{secnumdepth}{0}	% no section numbers

Hi there! It may have been days since I've caught up with you, or years, but either way I'm glad I can share with you what's going on in my life.

\subsection{So Brian, what's been going on in your life?}

Well, for a long time I was a grad student at UC Berkeley, as well as involved in my church. In June 2014, I finished my PhD in Nuclear Engineering, and started working as a postdoctoral researcher on the same project.

For a while, I've been questioning whether I want to continue on my current career track for the long term. As much as I enjoy scientific research, I long to do something that really makes a positive difference in the world, and I'm not sure research is the best way I can do that.

\subsection{What's this new career you mentioned?}

I'm planning to work on Bible translation! For some 180~million people in the world, speaking over 1800 different languages, the Bible does not exist in a language they can understand clearly.

\subsection{Seriously? How did that happen?}

Last Spring (2015), I was re-taking the \href{www.perspectives.org}{Perspectives} course on God's purpose and work through history and today. \ldots theology of all nations \ldots 

I hope I never shy away from \ldots evangelism \ldots but there are many important components in bringing the good news about Jesus to people who don't have an opportunity to hear \ldots

\subsection{What about that PhD you have?}

I've learned a lot over the past eight years in research, not only academically, but also about myself. I believe God has used my experiences to prepare me for the future. And I really don't know what the future holds - there are so many aspects of the task of Bible translation, and global missions, that I could find myself doing engineering, software work, or teaching.

Regardless, to be participating in God's purposes \ldots is more valuable to me than advancing my career \ldots (not that research isn't doing God's purposes \ldots)

\subsection{Okay. So what's it look like to be a Bible translator?}

The Bible has been translated into more than 1300 languages that are in use today. The ``low-hanging fruit'' of well-known (?) world languages already have Bibles. So the \ldots

\subsection{Well, alright then! So what happens now?}


\subsection{What can I do to support you?}

Pray!

\end{document}